---
title: "project3"
author: "lUis Hernandez Centti"
date: "Monday, October 13, 2014"
output: html_document
---

This is project 3 for is360. I selected the data package airquality and then added variables to make it a wider data. Then I filter day month with the a new variable called RealFEEL that was calculated from the formula to calculate the REeall feel sensation(apparent weather sensation), for that I needed to first find the Wind chill Temperature.

**Equation for Windchill:**

T{wc}=13.12 + 0.6215 T_a-11.37 V^{+0.16} + 0.3965 T_a V^{+0.16}

Twc = Wind Chill Temperature, Ta = Atmospheric Temperature (F), and V = Air Speed (mph) (Source).

**Equation to find the appararent temperature:**

the formula for the AT is: 
AT=T_a+0.348*e-0.70*ws+0.70\frac{Q}{ws+10}-4.25

```{r}
summary(airquality)
summmary(monthly)
```

First plot for the REal FEel monthly report:

```{r, echo=FALSE}
ggplot(airquality, aes(x=RealFeel)) +
geom_bar(width =.3)

Heres another way to plot it using barplot
barplot(t(as.matrix(monthly)), main="MONTHLY REAL FEEL",beside=TRUE)

```


then the second colored plot for the REal FEel monthly report:

```{r, echo=FALSE}
library("RColorBrewer")
coloredplot <- rev(colorRampPalette(brewer.pal(9, "RdYlBu"))(32))

filled.contour(t, v, rf , col=coloredplot, main="Monthly Real Feel",
nlevels=31, xlab="Temperature (??F)", ylab="Windspeed (mph)",
key.title=title("??F"), key.axes=axis(4, seq(-120, 40, by=20)),
zlim=c(-120,40))
```


**SOURCES**
To get the wind chill equation
http://planetcalc.com/2087/

to get the apparent temperature equation
http://planetcalc.com/2089/